---
title: "Austin, TX: Housing Prices"
subtitle: "Data Science 2 with R (STAT 301-2)"
author: "Christine Jie"
date: today

format:
  html:
    toc: true
    toc-depth: 4
    embed-resources: true
    code-fold: show
    link-external-newwindow: true
    
execute:
  warning: false
  
from: markdown+emoji

reference-location: margin
citation-location: margin
---

::: {.callout-tip icon="false"}
## Github Repo Link

[https://github.com/stat301-2-2024-winter/final-project-2-christinejie](https://github.com/stat301-2-2024-winter/final-project-2-christinejie)
:::

```{r}
#| echo: false
load(here::here("initial_processing/price"))
load(here::here("initial_processing/house_split.rda"))
```




## Introduction 
I wish to predict the sales price of houses in Austin, Texas using the models we learned this quarter. I used a data set from Kaggle called [Austin, TX House Listings](https://www.kaggle.com/datasets/ericpierce/austinhousingprices). 

My motivation for creating this model is because I truly enjoy browsing real estate websites in my free time. I have always been curious about the factors that influence the price of a home, including number of bedrooms, square footage, and quality of local schools. As an economics major, I'm also aware that housing prices are a large reflection of the local economy. 

The data set that I chose consists of over 15,000 home listings, including both categorical and numerical variables. 

## Data Overview
```{r}
#| echo: false
skimr::skim_without_charts(house)
```
There are no variables with any missingness. 
```{r}
#| echo: false
price_not_log
```
The `latest_price` variable my response variable. From this graph, we can see this variable is heavily right-skewed, so I decided to transform it using a log10 transformation. 

```{r}
#| echo: false
price_log
```
This is my new response variable that I will be working with for the rest of the project, `price_log10`, which is approximately normally distributed. 

## Methods


## Model Building and Selection 


## Final Model Analysis 


## Conclusion 


## References 


## Appendix EDA

