---
title: "Progress Memo 2"
subtitle: |
  | Final Project 
  | Data Science 2 with R (STAT 301-2)
author: "Christine Jie"
date: today

format:
  html:
    toc: true
    embed-resources: true
    
execute:
  echo: true
  warning: false

from: markdown+emoji 
reference-location: margin
citation-location: margin
---


::: {.callout-tip icon=false}

## Github Repo Link


[https://github.com/stat301-2-2024-winter/final-project-2-christinejie](https://github.com/stat301-2-2024-winter/final-project-2-christinejie)

:::


```{r}
library(tidyverse)
library(ggplot2)
house <- read_csv("data/austinHousingData.csv") |>
  janitor::clean_names() |>
  mutate(
    has_association = factor(has_association),
    has_cooling = factor(has_cooling),
    has_garage = factor(has_garage),
    has_heating = factor(has_heating),
    has_spa = factor(has_spa),
    has_view = factor(has_view),
    home_type = factor(home_type),
    city = factor(city),
    zipcode = factor(zipcode)
  ) |>
  select(-c(description, home_image))
```


## Prediction Problem 
I want to predict home sale prices in Austin, TX using variables including number of bedrooms, square feet, and neighborhood/zipcode. 


## Data source

[Austin, TX House Listings](https://www.kaggle.com/datasets/ericpierce/austinhousingprices)
My data source is Kaggle. 


## Data quality & complexity check

```{r}
ncol(house)
nrow(house)
```
There are 45 variables and 15,171 observations 

There are 12 categorical and 33 numerical variables. 
```{r}
is.na(house) |>  
  head(n=3)
```

There are no missingness issues. 

## Target Variable Analysis 

```{r}
house |> 
  ggplot(aes(x=latest_price)) + 
  geom_histogram(bins=500) +
  coord_cartesian(xlim=c(0,700000))
```

The latest_price variable is approximately normally distributed when disregarding outliers. Above, I limited x values to 700,000, but I need to think about what to do about outliers in my analysis. 


```{r}
house |> 
  ggplot(aes(x=latest_price, y= living_area_sq_ft)) + 
  geom_jitter() +
  coord_cartesian(xlim=c(0,700000), ylim=c(0,5000)) + 
  geom_smooth()
```
Price and square feet are generally positively correlated. As square footage increases, so does price. However, this positive relationship is weakened when outliers are considered. Again, this is something I need to consider going forward.  

