---
title: "Progress Memo 2"
subtitle: |
  | Final Project 
  | Data Science 2 with R (STAT 301-2)
author: "Christine Jie"
date: today

format:
  html:
    toc: true
    embed-resources: true
    
execute:
  echo: false
  warning: false

from: markdown+emoji 
reference-location: margin
citation-location: margin
---
```{r}
#| echo: false

load(here::here("results/house.rda"))
load(here::here("results/house_split.rda"))
load(here::here("results/house_folds.rda"))
load(here::here("results/house_recipe.rda"))
load(here::here("results/null.rda"))
load(here::here("results/lm.rda"))
load(here::here("results/rmse_table.rda"))
library(tidyverse)
library(rsample)
library(parsnip)
library(tidymodels)
library(glmnet)
library(ranger)
library(kknn)
library(kableExtra)
set.seed(123)
library(here)
tidymodels_prefer()
library(doMC)
num_cores <- parallel::detectCores(logical=TRUE)
registerDoMC(cores=num_cores)
```




::: {.callout-tip icon=false}

## Github Repo Link

[https://github.com/stat301-2-2024-winter/final-project-2-christinejie](https://github.com/stat301-2-2024-winter/final-project-2-christinejie)

:::

**Data Source**: [Austin, TX House Listings](https://www.kaggle.com/datasets/ericpierce/austinhousingprices)
From Kaggle. 

**Project Overview**: I want to predict house sale prices in Austin using variables such as number of bathrooms, number of bedrooms, and square feet of living space. This is a regression problem. 

**Assessment Metric**: I will use RMSE to evaluate each model. 

**Analysis Plan**

Data Splitting: used prop = 0.75, strata = price_log10, breaks = 4. See `1_initial_setup.R`

Resampling: used vfold_cv with 10 folds and 5 repeats. See `1_initial_setup.R`

Model Types: planning on using baseline, null, lasso, ridge, logistic, random forest, boosted tree. See `3_baseline.R` and `3_OLS.R`

Recipes: planning on creating 2 recipes: one standard and one tree based recipe. See `2_recipes.R`

**Progress Summary**

1) Determined that variable of interest "latest_price" should be transformed using a base 10 log transformation. New outcome variable of interest is "pricelog_10". See `1_initial_setup.R`. 

2) Split and folded "house" dataset. See `1_initial_setup.R`. 

3) Created 2 recipes, one standard and one for tree based models. Used several interaction terms for standard recipe. For both recipes, handled zero variance, dummy variables, and normalized/centered/scaled. See `2_recipes.R`. 

4) Defined and fit baseline/null and simple linear models using the standard recipe. Calculated RMSE for each model. See `3_baseline.R` and `3_OLS.R`. 

5) Created a table showing RMSE for each model. See `4_model_results.R`. 

**RMSE Table for Baseline and Linear Models**
```{r}
#| echo: false
rmse_table
```


**Next Steps**

1) Continue developing recipe, especially pay attention to interaction terms 

2) Define and fit additional models as specified above 

3) Calculate RMSE for each model. 

4) Determine best model using metrics. 

**Issues/Concerns**

1) Unsure of how to determine which variables need `step_interact()`

2) I have very large data set and it takes a long time to run most things, I am using parallel processing but it's still taking a long time 


